### 2013-06-18 replies.tex

\documentclass [12pt,onecolumn,twoside,openright]{report}
\usepackage[utf8]{inputenc} \usepackage[T1]{fontenc} \usepackage[top=2.4cm,
bottom=2.4cm, left=2.4cm, right=2.4cm]{geometry} \usepackage{setspace}
\usepackage{color}

\begin{document} \begin{onehalfspacing} \begin{center} \large{Response to
Reviewer: Inferring food web structure from predator-prey body size
relationships} \end{center}

Dominique Gravel, Timoth\'ee Poisot, Camille Albouy, Laure Velez, David Mouillot
\begin{center} Reviewer 2: \end{center}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We do agree that using phylogenetic information should help improve the technique much beyond what we actually do. This is why we made a mention of this opportunity toward the end of the discussion. But it's right we only mentionned it and did not developped our ideas any further. We added the following lines (LXXX) to the discussion:}}

\textcolor{blue}{Bayesian inference appears a good candidate to achieve goal. It offers the possibility to constrain the prior distribution of the likelihood of any pairwise interaction, based on trait matching, using alternative source of data. The method we employed here was based on the match between predator and prey traits. This method could be generalized by looking at the match between all potential traits. Eklof et al. (2013) indeed found that the match between only three traits is enough to encompass a vast majority of interactions. But when such data is not always available, then it might be possible to use phylogeny as a proxy for a high dimensional trait species, provided that traits are conserved along the phylogeny (Mouquet et al. 2012). A bayesian addition to the model would be to weight the likelihood that species $j$ is a predator of species $i$, considering that the closest relative of this predator is also a predator of $i$. It could account for part of the unexplained variation we found in our analysis, for instance by constraining the range of the diet for some large predators or by creating holes within the feeding range (Rall et al. 2011).}

%---------------% 
\medskip \textbf{Comment}: The three regression lines in Fig.
2 demonstrate the mean, maximum and minimum prey size of a predator. I found
this quite intriguing that for a given meta-community, this would predict how
the number of links to resources (the generality of the predator) and the number
of links to consumers (the vulnerability of a resource) depend on the body-mass
on the x-axis of the figure. We have analyzed these relationship for a variety
of food webs (Digel et al. 2011), but I could imagine that the methods
introduced here would allow a more thorough investigation of this relationship.
If possible, a general graph showing the relationship between generality and
predator body mass would be very interesting to see.

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{This is certainly an intriguing result coming out from our analysis. We also find this result interesting because it links to some of our previous work on persistence in metacommunities and our current work on the biogeography of body size. We also had a discussion with Neo Martinez at a previous workshop about this relationship, he was curious to see if his assumption of a linear relationship between the niche and the range of the diet was confirmed (Williams and Martinez, 2000). There are already a large number of figures in the paper (6) so we prefer not to add a new one, that could already be guessed from the Fig. 2. We however added the following discussion (at PXLX):}}

\textcolor{blue}{It appears at Fig. 2 that the feeding range increases with the body size of the predator. This result was quite general across datasets with a good fit of the predator-prey body size relationship, although with considerable variation in the slope of the relationship. It offers the possibility to compare empirical based estimates of the parameters to the original niche model of Williams (2011). For this specific dataset that the model for the centroid is $c_i = -1.34 + 0.66n_i$ and the average range ($\overline{r}_i=(r_{high,i} - r_{low,i})/2$) is $\overline{r}_i = 0.63 + 0.78n_i$. The original niche models assumed that $r_i$ scales linearly with connectance $C$ and the niche position, such that $r_i = 2Cn_i$. Even though the parameterization suggests a linear increase of generality with body size, the final number of preys in the diet for a given size will depend on the frequency distribution of body size. A large predator for instance could have a large feeding range, but only few species to find on and effectively appears as a specialist. This relationship will have to be investigated further, among several food webs (e.g. Digel et al. 2011), because the scaling of generality with trophic rank has several consequences on persistence (Gravel et al. 2011) and food web dynamics (e.g. Brose et al. 2006, Berlow et al. 2009).}

%---------------% 
\medskip \textbf{Comment}: The decrease of the fraction of
potential links that are realized from local to landscape scales was the central
topic of one of our prior projects (Brose et al. 2004). You might find this
useful to support your assumption that meta-communities should include links
that are not realized at local scales – and meta food webs should thus contain
more links than the sum of the local food webs. This is exactly the pattern that
we documented for different types of ecosystems.

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We fully agree with this result, it was also the central motivation for our investigations in a recent paper by Gravel et al. (2011, Ecology Letters). We hypothesized that this difference was the result of extinction-colonization dynamics, promoting the persistence of the most generalist species in local communities. It is however hard to figure out where to put this result in the current manuscript. We are currently working on a theory for metawebs, trying to develop a framework to improve inference of local web structure given the probability of the interactions in the metaweb. This approach considers the likelihood of an interaction between a pair of species given their co-occurrence andfavorable environmental conditions. This topic is however beyond the topic of the current paper. In fact, it goes the other way around. We need information on trait-matching to predict potential interactions in the metaweb (the topic of the current ms), and then a theory for sampling the metaweb.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected
accordingly by replacing the abbrevation B by M}}

@@

\begin{center} Reviewer 3: \end{center}

@@

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{As stated
in the abstract, our method allows to ``infer the matrix of potential
interactions among a pool of species'', and does so regardless of whether one is
working at the local or regional scale. In the text, we give examples at both
these scales (locally in figures 2 and 3, regionaly in figure 5). We do agree
with the fact that additional information will make the predictions better; this
is described at length in the text, and an example of this (including
co-occurence along the depth gradient) is pictured in Fig. 5b. This is also
explicitly written in the discussion (L. XXX-XXX). We corrected the abstract and the last paragraph of the introduction to make clear that our metholody applies at both the local and metaweb scales.}}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The study of Rohr et al. (2010), does not allow to evaluate the parameters of a new species entering a local community, neither the metaweb (which is the object of the current study). It is therefore not possible to infer the potential links an immigrating species will do with the resident species. These methods also require a complete knowledge of the interactions in the community. Our method is consequently much more robust than previous methods to infer the parameters of the niche model. Based on these arguments, we believe that the method  will be used for instance to study the interactions in emerging communities following global changes.}}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We do agree that the best statistical model for this analysis should be a type 2 regression. We however deliberately used a type 1 regression for two reasons: i) we needed the R2 of the model to perform the analysis of predictive performance (Fig. 3). ii) we are not aware of any quantile regression that could account for uncertainty in the independent variable. We added a mention to this issue at LXXX.}}

%---------------% 
\medskip l.50: The use of "emergent" sounds strange here.
Please clarify.

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{ We replaced the word "emergent" by "novel".}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We modified the sentence to avoid amiguities. The metaweb gives interactions among a given set of species, wether at local or regional scales.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{See the above responses to previous comments.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{This is a basic
postulate of the niche model. We have added a reference to the original paper to
eliminate ambiguity.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The
  \emph{dotted} lines. We corrected accordingly and apologize for the mistake.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{These are the parameters of the linear quantile regressions. The sentence was corrected accordingly.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{No. The centroid
is a function of the two body sizes (hence $\alpha$), while the range limits are
a function of the predator body size and its range.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{Whether the
correct prediction of absence or presence of an interaction is the most
interesting part of a model is ultimately a matter of personal taste, and
adequation to the study objectives. Given that (especialy when no other traits
than body size are included), this method tends to over-estimate the number of
links, we argue that correctly predicting absences of links is an extremely
important feature.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected
accordingly.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We argue it is an
important piece of information, which was required by a previous reviewer. We
made no changes.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The choice of quantiles are left free to the user in the R code providing with this article, by default, we chose the most commonly used threshold of 5\% and 95\%. A threshold of 100\% would include all interactions, but would tend to overpredict the link density.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected accordingly and apologize for the mistake}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The $c$ is
constrained by $n$ in the original niche model: it is drawn uniformly
between $r/2$ and $n$, with the expected value of $r$ being $2Cn$.}}

\textit{\textcolor{blue}{The fact that our model over-predict the number of
interactions is discussed in the manuscript (along with why, and how to overcome
it). However, the purposes of the two models are not the same. The niche model
allows to generate a distribution of network properties based only on
connectance and richness. We add allometric informations so as to be able to
estimate species-level interactions in addition to network properties. The
allometric relationshipss on which we rely are well documented. As for the fact
that other traits can be added, this is discussed in the manuscript at several
places, including a figure. }}

>>>>

\documentclass [12pt,onecolumn,twoside,openright]{report}
\usepackage[utf8]{inputenc} \usepackage[T1]{fontenc} \usepackage[top=2.4cm,
bottom=2.4cm, left=2.4cm, right=2.4cm]{geometry} \usepackage{setspace}
\usepackage{color}
\usepackage[style=bes]{biblatex}
\bibliography{./library}

\begin{document} \begin{onehalfspacing} \begin{center} \LARGE{Response to
Reviewer: Inferring food web structure from predator-prey body size
relationships} \end{center}

\medskip

Dominique Gravel, Timoth\'ee Poisot, Camille Albouy, Laure Velez, David Mouillot

\medskip
\begin{center} \large{Reviewer 2: }\end{center}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We do agree that using phylogenetic information should help improve the technique much beyond what we actually do. This is why we made a mention of this opportunity toward the end of the discussion. But it's right we only mentioned it and did not developed our ideas any further. We added the following lines (Lines 375-389) to the discussion:}}

\medskip \textcolor{blue}{Bayesian inference appears a good candidate to achieve goal. It
offers the possibility to constrain the prior distribution of the likelihood of
any pairwise interaction, based on trait matching, using alternative source of
data. The method we employed here was based on the match between predator and
prey traits. This method could be generalized by looking at the match between
all potential traits. \textcite{Eklof2013} indeed found that the match between
only three traits is enough to encompass a vast majority of interactions. But
when such data is not always available, then it might be possible to use
phylogeny as a proxy for a high dimensional trait species, provided that traits
are conserved along the phylogeny \parencite{Mouquet2012}. A bayesian addition
to the model would be to weight the likelihood that species $j$ is a predator of
species $i$, considering that the closest relative of this predator is also a
predator of $i$. It could account for part of the unexplained variation we found
in our analysis, for instance by constraining the range of the diet for some
large predators or by creating holes within the feeding range
\parencite{Rall2011}}

%---------------% 
\medskip \textbf{Comment}: The three regression lines in Fig.
2 demonstrate the mean, maximum and minimum prey size of a predator. I found
this quite intriguing that for a given meta-community, this would predict how
the number of links to resources (the generality of the predator) and the number
of links to consumers (the vulnerability of a resource) depend on the body-mass
on the x-axis of the figure. We have analyzed these relationship for a variety
of food webs \parencite{Digel2011}, but I could imagine that the methods
introduced here would allow a more thorough investigation of this relationship.
If possible, a general graph showing the relationship between generality and
predator body mass would be very interesting to see.

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{This is certainly an intriguing result coming out from our analysis. We also find this result interesting because it links to some of our previous work on persistence in meta-communities and our current work on the biogeography of body size. We also had a discussion with Neo Martinez at a previous workshop about this relationship, he was curious to see if his assumption of a linear relationship between the niche and the range of the diet was confirmed  \parencite{Williams2000}. There are already a large number of figures in the paper (6) so we prefer not to add a new one, that could already be guessed from the Fig. 2. We however added the following discussion (at Page 14-15; Lines 331-346):}}

\medskip\textcolor{blue}{It appears at Fig. 2 that the feeding range increases with the body size of the predator. This result was quite general across datasets with a good fit of the predator-prey body size relationship, although with considerable variation in the slope of the relationship. It offers the possibility to compare empirical based estimates of the parameters to the original niche model of Williams (2011). For this specific dataset that the model for the centroid is $c_i = -1.34 + 0.66n_i$ and the average range ($\overline{r}_i=(r_{high,i} - r_{low,i})/2$) is $\overline{r}_i = 0.63 + 0.78n_i$. The original niche models assumed that $r_i$ scales linearly with connectance $C$ and the niche position, such that $r_i = 2Cn_i$. Even though the parameterization suggests a linear increase of generality with body size, the final number of preys in the diet for a given size will depend on the frequency distribution of body size. A large predator for instance could have a large feeding range, but only few species to find on and effectively appears as a specialist. This relationship will have to be investigated further, among several food webs (e.g. \textcite{Digel2011}), because the scaling of generality with trophic rank has several consequences on persistence \parencite{Gravel2011b} and food web dynamics \parencite{Brose2006,Berlow2009}.}

%---------------% 
\medskip \textbf{Comment}: The decrease of the fraction of
potential links that are realized from local to landscape scales was the central
topic of one of our prior projects Brose et al. 2004. You might find this
useful to support your assumption that meta-communities should include links
that are not realized at local scales – and meta food webs should thus contain
more links than the sum of the local food webs. This is exactly the pattern that
we documented for different types of ecosystems.

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We fully agree with this result, it was also the central motivation for our investigations in a recent paper by Gravel et al. (2011, Ecology Letters). We hypothesized that this difference was the result of extinction-colonization dynamics, promoting the persistence of the most generalist species in local communities. It is however hard to figure out where to put this result in the current manuscript. We are currently working on a theory for metawebs, trying to develop a framework to improve inference of local web structure given the probability of the interactions in the metaweb. This approach considers the likelihood of an interaction between a pair of species given their co-occurrence and favorable environmental conditions. This topic is however beyond the topic of the current paper. In fact, it goes the other way around. We need information on trait-matching to predict potential interactions in the metaweb (the topic of the current ms), and then a theory for sampling the metaweb.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected
accordingly by replacing the abbreviation B by M}}

@@

\newpage
\begin{center} {\large Reviewer 3:} \end{center}

@@

\medskip 
\medskip \textbf{\large{Main comments:}}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{As stated
in the abstract, our method allows to ``infer the matrix of potential
interactions among a pool of species'', and does so regardless of whether one is
working at the local or regional scale. In the text, we give examples at both
these scales (locally in figures 2 and 3, regionally in figure 5). We do agree
with the fact that additional information will make the predictions better; this
is described at length in the text, and an example of this (including
co-occurence along the depth gradient) is pictured in Fig. 5b. This is also
explicitly written in the discussion (Lines  319-322). We corrected the abstract and the last paragraph of the introduction to make clear that our methodology applies at both the local and metaweb scales.}}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The study of  \textcite{Rohr2010}, does not allow to evaluate the parameters of a new species entering a local community, neither the metaweb (which is the object of the current study). It is therefore not possible to infer the potential links an immigrating species will do with the resident species. These methods also require a complete knowledge of the interactions in the community. Our method is consequently much more robust than previous methods to infer the parameters of the niche model. Based on these arguments, we believe that the method  will be used for instance to study the interactions in emerging communities following global changes.}} 
\medskip

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We do agree that the best statistical model for this analysis should be a type 2 regression. We however deliberately used a type 1 regression for two reasons: i) we needed the R2 of the model to perform the analysis of predictive performance (Fig. 3). ii) we are not aware of any quantile regression that could account for uncertainty in the independent variable. We added a mention to this issue at Lines 167-168.}}
\medskip 
%---------------%

\medskip l.50: The use of "emergent" sounds strange here.
Please clarify.

\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{ We replaced the word "emergent" by "novel".}}

@@

\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We modified the sentence to avoid ambiguities. The metaweb gives interactions among a given set of species, wether at local or regional scales.}}

@@

\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{See the above responses to previous comments.}}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{This is a basic
postulate of the niche model. We have added a reference to the original paper to
eliminate ambiguity.}}

@@

\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The
  \emph{dotted} lines. We corrected accordingly and apologize for the mistake.}}

@@

\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{These are the parameters of the linear quantile regressions. The sentence was corrected accordingly.}}

@@

\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{No. The centroid
is a function of the two body sizes (hence $\alpha$), while the range limits are
a function of the predator body size and its range.}}
`
\medskip

@@

\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{Whether the
correct prediction of absence or presence of an interaction is the most
interesting part of a model is ultimately a matter of personal taste, and
adequation to the study objectives. Given that (especially when no other traits
than body size are included), this method tends to over-estimate the number of
links, we argue that correctly predicting absences of links is an extremely
important feature.}}
\medskip

@@

\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected
accordingly.}}

@@

\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We argue it is an
important piece of information, which was required by a previous reviewer. We
made no changes.}}

@@

\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The choice of quantiles are left free to the user in the R code providing with this article, by default, we chose the most commonly used threshold of 5\% and 95\%. A threshold of 100\% would include all interactions, but would tend to overpredict the link density.}}

@@

\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected accordingly and apologize for the mistake}}

@@

\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The $c$ is
constrained by $n$ in the original niche model: it is drawn uniformly
between $r/2$ and $n$, with the expected value of $r$ being $2Cn$.}}

\medskip\textit{\textcolor{blue}{The fact that our model over-predict the number of
interactions is discussed in the manuscript (along with why, and how to overcome
it). However, the purposes of the two models are not the same. The niche model
allows to generate a distribution of network properties based only on
connectance and richness. We add allometric informations so as to be able to
estimate species-level interactions in addition to network properties. The
allometric relationships on which we rely are well documented. As for the fact
that other traits can be added, this is discussed in the manuscript at several
places, including a figure. }}

\newpage
 \printbibliography
